\bf Forecasts Reconciliation: A geometric view with new insights on bias correction.

### 2019-08-17 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
new first paragraph

>>>>

	The past decade has seen rapid development in methodology for forecasting time series that adhere to linear aggregation constraints.  Of particular prominence have been {\em forecast reconciliation} methods involving two steps; first separate forecasts are produced for all series, then these are adjusted ex post to ensure coherence with the linear constraints.  Forecast reconciliation has mostly been formulated as a regression model, see \cite{Hyndman2011} and \cite{WicEtAl2019} for examples.  This setup can be counter-intuitive since a vector of forecasts coming from different time series models is also assumed to be the dependent variable in a regression model.  In this paper, we eschew a regression interpretation in favour of a novel, geometric understanding of forecast reconciliation.  In doing so, we review and provide clearer insight into existing approaches, and achieve a clearer understanding of the interplay between forecasts bias and reconciliation methods.
